TacticToe: Learning the Game of Tactics

### 2018-02-13 tactictoe_jv.tex
Sec 2
Start sec 3

The different components of \tactictoe revolves around the concept of a
search tree. The following definitions are made relative to a static search
tree, the description of its evolution during proof search will be given in
Section~\ref{sec:proofsearch}.

@@

some text to add here.

@@

\section{Prediction}\label{s:prediction}
The learning-based selection of relevant lemmas significantly improves the
automation for hammers~\cite{BlanchetteGKKU16}. In \tactictoe, we adapt
one of the strongest lemma selection
methods: the modified distance-weighted \emph{$k$ nearest-neighbour}
classifier~\cite{ckju-pxtp13,DudaniS76} to predict three different objects:
 tactics, theorems and list of goals. The number of predicted objects $k$ is
 called the prediction radius.

@@

\paragraph{Tactics}
To start with, we build a database of tactics consisting
of tactic-goal pairs recorded from successful tactic applications in human
proofs (see
Section~\ref{sec:recording}).
Then, during proof search, we order recorded goals according to their
similarity with a targeted goal $g$ (usually the first pending goal of a node).
This induces
through the recorded pairs an
order on tactics. The intuition is that tactics which have been successful on
goals similar to $g$ should be tried first, since they are more likely to lead
to a proof.
This predicted tactic order is translated into a prior policy for our MCTS
algorithm (see Section~\ref{sec:policy}).
Tactic selection is also used to improve the quality of the database
of tactics during orthogonalization (see Section~\ref{sec:ortho}).

\paragraph{Theorems as Argument of Tactics}
We first collect a set of theorems for our theorem predictor to select from.
It includes the \holfour theorem database and theorems from the local namespace.
Predicted tactics during proof search and orthogonalization may include
tactics where arguments (list of theorems) have been erased (see Section
\ref{sec:synthesis}).
We instantiate those tactics by theorems that are syntactically the closest to
the targeted goal as they are more likely to help.
The same algorithm selects suitable premises for ATPs integrated with
\tactictoe (see Section~\ref{sec:atp}).

@@

\subsection{Feature Extraction}\label{sec:features}
The three objects considered are different representation of mathematical
formulas. Therefore, we start by describing features for terms. From there, we 
extend the extraction mechanism
to goals, theorems and lists of goals. Duplicated features are always removed
so that each object has an associated set of features.

>>>>

The different components of \tactictoe revolve around the concept of a
search tree. The following definitions are made relative to a static search
tree, the description of its evolution during proof search will be given in
Section~\ref{sec:proofsearch}.

@@

\todoi{some text to add here}

@@

\section{Prediction}\label{s:prediction}
The learning-based selection of relevant lemmas significantly improves the
automation for hammers~\cite{BlanchetteGKKU16}. In \tactictoe, we use the
distance-weighted \emph{$k$ nearest-neighbour} classifier~\cite{DudaniS76}
adapted for lemma selection~\cite{ckju-pxtp13}. It allows for hundreds of
predictions per second, while maintaining very high prediction quality~\cite{femalecop}.
Here it is used
to predict three different kinds of objects:
 tactics, theorems and list of goals. The number of predicted objects $k$ is
 called the \emph{prediction radius}.

@@

\paragraph{Tactics}
To start with, we build a database of tactics consisting
of tactic-goal pairs recorded from successful tactic applications in human
proofs (see
Section~\ref{sec:recording}).
Then, during proof search, we order recorded goals according to their
similarity with a targeted goal $g$ (usually the first pending goal of a node).
The recorded pairs induce an
order on tactics. The intuition is that tactics which have been successful on
goals similar to $g$ should be tried first, since they are more likely to lead
to a proof.
This predicted tactic order is translated into a prior policy for our MCTS
algorithm (see Section~\ref{sec:policy}).
Tactic selection is also used to improve the quality of the database
of tactics during orthogonalization (see Section~\ref{sec:ortho}).

\paragraph{Theorems as Arguments of Tactics}
We first collect a set of theorems for our theorem predictor to select from.
It includes the \holfour theorem database and theorems from the local namespace.
Predicted tactics during proof search and orthogonalization may include
tactics where arguments (list of theorems) have been erased (see Section
\ref{sec:synthesis}).
We instantiate those tactics by theorems that are syntactically the closest to
the goal as they are more likely to help.
The same algorithm selects suitable premises for ATPs integrated with
\tactictoe (see Section~\ref{sec:atp}).

@@

\subsection{Feature Extraction}\label{sec:features}
All the three kinds of considered objects to predict correspond to (different representations of)
mathematical
formulas. Therefore, we start by describing features for terms. From there, we
extend the extraction mechanism
to goals, theorems and lists of goals. Duplicated features are always removed
so that each object has an associated set of features.
